Making Sequential Programs Deterministic

### 2019-04-06 design.tex
Remove repetition

\OurTypeSystem supports parametric
polymorphism~\cite{Abadi:1989:FIM:77350.77373,Plotkin:1993:LPP:645891.671433}
over both classes and methods.
A polymorphic abstraction (a class or method) is written and
typechecked once.
It acts as if it has multiple different types, and each use site is
typechecked using the most specific applicable instantiated
non-polymorphic type.

\OurTypeSystem supports both basetype polymorphism and qualifier polymorphism.
When both are applied, it gives the effect of type polymorphism.
Polymorphism applies to both classes and methods.

>>>>

\OurTypeSystem supports parametric
polymorphism~\cite{Abadi:1989:FIM:77350.77373,Plotkin:1993:LPP:645891.671433}.
A polymorphic abstraction (a class or method) is written and
typechecked once.
It acts as if it has multiple different types, and each use site is
typechecked using the most specific applicable instantiated
non-polymorphic type.

\OurTypeSystem supports both basetype polymorphism and qualifier polymorphism.
When both are applied, it gives the effect of type polymorphism.
